Capturing the geometric structure of our experiences and how we remember them

### 2018-07-23 main.tex
brain plot figure legend

\begin{figure}[]
\centering
\includegraphics[width=1\textwidth]{figs/6_brains.pdf}
\caption{\small \textbf{Recall model searchlight analysis.} A 2-dimensional embedding of the best fitting line segment model.  The points outlined in black represent and connected by black line segments represent the critical recall events (or ``hinge-points'') of the best fitting model colored according to their matching video event.  The points not outlined in black are individual participant recall event topic vectors colored by the most similar video event. The kernel density plot represents the distribution across all points.  The word clouds for hinge-point (left: video; right: recall) were created by plotting the top 100 words from topic model that were ``activated'' during a particular event.}
\label{fig:topics}
\end{figure}

>>>>

\begin{figure}[]
\centering
\includegraphics[width=1\textwidth]{figs/6_brains.pdf}
\caption{\small \textbf{Recall model searchlight analysis.} A). We used dynamic time warping to separately align each participant's recall model to the video model. The left matrix is S13's video-recall correlation matrix before warping. The yellow stars represent the path recovered by dynamic time warping. The right matrix is the result after warping. The same warping path was applied to the fMRI timeseries (separately for each participant). Below the matrices are toy examples representing a vectorized (aligned) recall correlation matrix and a vectorized (aligned) fMRI searchlight correlation matrix. These vectors were correlated for each searchlight sphere in the brain to assess brain regions whose temporal correlation structure mirrored the participant's recall model correlation structure. B) A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix. Significance threshold (p<.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
\label{fig:topics}
\end{figure}
